---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

**Principles of Data Visualization and Introduction to ggplot2**

I have provided you with data about the 5,000 fastest growing companies in the US, as compiled by Inc. magazine. lets read this in:

```{r}

inc <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA_608/master/module1/Data/inc5000_data.csv", header= TRUE)


```

And lets preview this data:

```{r}

head(inc)

```
```{r}

summary(inc)

```

Think a bit on what these summaries mean. Use the space below to add some more relevant non-visual exploratory information you think helps you understand this data:

```{r}

# Insert your code here, create more chunks as necessary

suppressMessages(library(dplyr))
library(ggplot2)
library(forcats)


```

## Question 1

Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use. This visualization is ultimately going to be consumed on a 'portrait' oriented screen (ie taller than wide), which should further guide your layout choices.

```{r}
# Answer Question 1 here

inc %>%   
  mutate(state= fct_infreq(inc$State)) %>% 
    ggplot( aes(x=state)) +
    geom_bar(fill = 'lightblue' ) +
    coord_flip() +
    theme_bw() +
    theme( axis.text.y = element_text( size =rel(0.7), angle = 0 )) +
    ggtitle("Fastest growing company US") +
    xlab('State') +
    ylab(' Number of Companies by State ')

```

By observing the graph we can appreciate that the state of California is the one that has the fastest growing companies.













## Quesiton 2

Lets dig in on the state with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by companies in different industries. Create a plot that shows the average and/or median employment by industry for companies in this state (only use cases with full data, use R's `complete.cases()` function.) In addition to this, your graph should show how variable the ranges are, and you should deal with outliers.

```{r}

# Answer Question 2 here

inc %>% filter(State == 'NY') %>% filter(complete.cases(.)) %>%   
    ggplot( aes(x=Industry, y=Employees)) +
    geom_boxplot(fill = 'lightblue', outlier.colour = NA ) +
    coord_flip(ylim = c(0, 800), expand = T) +
    theme_minimal() +
    stat_summary(fun.y = "mean", colour = "darkorange", size = 1, geom = "point") +
    ggtitle("Employees by NY states Indutries") +
    xlab('Industry') +
    ylab("")
```

In the graph with can see some outliers which affect the mean of employees.One solution is that we dont show the Outlier in the graph.
## Question 3

Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart that makes this information clear. Once again, the distribution per industry should be shown.

```{r}

# Answer Question 3 here


 inc %>% group_by(Industry) %>% summarise(mean = mean(Revenue),n =n()) %>% 
    ggplot( aes(x=reorder(Industry,mean),y=mean), stat = "identity") +
    geom_col(fill = 'lightblue' ) +
    coord_flip() +
    theme_bw() +
    ggtitle("New York Average Revenue by employees ") +
    xlab('Industry') +
    ylab(' ')

```

We can see that Computer Hardware has the highest mean revenue 

